The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars

### 2019-03-22 paper/ms.tex
apj format

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

@@

% added by DH
\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
\newcommand{\Dnu}{\mbox{$\Delta \nu$}\xspace}
\newcommand{\dnu}{\mbox{$\delta \nu$}\xspace}
\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
\newcommand{\logg}{\mbox{$\log g$}\xspace}
\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
\newcommand{\msun}{\mbox{$\mathrm{M}_{\sun}$}\xspace}
\newcommand{\rsun}{\mbox{$\mathrm{R}_{\sun}$}\xspace}
\newcommand{\kepler}{\textit{Kepler}\xspace}
\newcommand{\ktwo}{\textit{K2}\xspace}
\newcommand{\hipparcos}{\textit{Hipparcos}\xspace}
\newcommand{\gaia}{\textit{Gaia}\xspace}

@@

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

\title[The Kepler Smear Campaign]{The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars}

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6}$
Timothy R. White,$^{7,5}$\newauthor
Amalie Stokholm,$^{5}$
Allyson Bieryla,$^{8}$
David W. Latham,$^{8}$
Madeline Lucey,$^{6}$\newauthor
Conny Aerts,$^{9,10}$
Suzanne Aigrain,$^{3}$ 
Victoria Antoci,$^{5}$
Timothy R. Bedding,$^{11,5}$\newauthor
Dominic M. Bowman,$^{9}$
Ashley Chontos,$^{12}$
Gilbert A. Esquerdo,$^{8}$
Daniel Huber,$^{12}$\newauthor
Paula Jofr\'{e},$^{13}$
Simon J. Murphy,$^{11,5}$
Timothy van Reeth,$^{11,5}$
Victor Silva Aguirre,$^{5}$\newauthor
Jie Yu$^{11,5}$ 
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{8}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{9}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
$^{10}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
$^{11}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{12}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{13}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

\pubyear{2018}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this paper, aside from publishing the light curves of these stars, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 33 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars. We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample. \href{https://github.com/benjaminpope/smearcampaign}{\faGithub}
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
asteroseismology -- techniques: photometric -- stars: variable: general
\end{keywords}

@@

\input{quarters.tex}

@@

\begin{figure*}
\noindent\includegraphics[width=15cm,keepaspectratio]{gaia_kepler_hr.png}

@@

\begin{figure}
\noindent\includegraphics[width=8cm,keepaspectratio]{contam_HD_181778.png}

\caption{\label{contamination}
Power spectra of odd and even quarters of HD~181778. It is clear from inspection that while odd quarters have the power spectrum expected of a giant star, even quarters have very high amplitude coherent oscillations.}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=8cm,keepaspectratio]{contam.eps}

@@

\input{all_stars.tex}
\input{all_Stars2.tex}

@@

\input{astero_table.tex}

@@

\input{stellar_props.tex}

\input{abundances_1.tex}
\input{abundances_2.tex}

@@

The spectroscopic properties are the effective temperature \teff, the metallicity \feh, and the surface gravities \logg from Table~\ref{stellar_props}. These are accompanied by the global asteroseismic properties \Dnu and \numax from Table~\ref{astero_table}. Theoretical predictions of \Dnu and \numax were computed using the asteroseismic scaling relation for any point along an evolutionary track or isochrone. For the solar values, we adopted $\nu_{\text{max, }\odot}=3090$~$\mu$Hz, $\Delta\nu_{\odot}=135.1$~$\mu$Hz \citep{huber2011}, and $T_{\text{eff, }\odot}=5777$~K.
\newpage

@@

\begin{figure}
% \noindent\includegraphics[width=17cm,keepaspectratio]{different_constraints_fullsample_ove02.pdf}
\noindent\includegraphics[width=8.5cm,keepaspectratio]{different_constraints_ben.pdf}

@@

\begin{figure}
\noindent\includegraphics[width=8.5cm,keepaspectratio]{combined_radii.eps}

@@

\begin{figure*}
\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{Pope_alpha_oddZ.pdf}

@@

In addition, to the $\alpha$ and odd-Z elements we also derived the chemical abundance for several neutron capture elements including Sr, Zr, La, Eu (left panel of Fig~\ref{fig:ncap}) as well as Y, Ba, and Nd (right panel of Fig.~\ref{fig:ncap}).  It is clear from Fig.~\ref{fig:ncap}  that the chemical abundance ratio of each neutron capture element is consistent with the Galactic disk population. The Ba of our sample is slightly enhanced, however, while the Y of our sample is slightly reduced relative to the general disk population of \cite{Bensby2014}. Nevertheless, we conclude all elemental abundance ratios studied our sample most closely resemble the Galactic disk. 
\begin{figure*}
\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{Pope_ncap.pdf}

@@

\begin{figure*}
\noindent\includegraphics[width=19cm,keepaspectratio]{HD_183124.png}

@@

\begin{figure*}
\noindent\includegraphics[width=19cm,keepaspectratio]{HD186255_time-delay_plot.png}

@@

\bibliographystyle{mnras}
\bibliography{ms} % if your bibtex file is called example.bib

@@

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
% \documentclass[a4paper,fleqn,usenatbib]{mnras}
\documentclass[modern]{aastex62}

@@

% added by DH
\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
\newcommand{\Dnu}{\mbox{$\Delta \nu$}\xspace}
\newcommand{\dnu}{\mbox{$\delta \nu$}\xspace}
\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
\newcommand{\logg}{\mbox{$\log g$}\xspace}
\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
\newcommand{\msun}{\mbox{$\mathrm{M}_{\sun}$}\xspace}
\newcommand{\rsun}{\mbox{$\mathrm{R}_{\sun}$}\xspace}
\newcommand{\kepler}{\textit{Kepler}\xspace}
\newcommand{\ktwo}{\textit{K2}\xspace}
\newcommand{\hipparcos}{\textit{Hipparcos}\xspace}
\newcommand{\gaia}{\textit{Gaia}\xspace}
\definecolor{linkcolor}{rgb}{0.1216,0.4667,0.7059}

\usepackage{xcolor, fontawesome}
\definecolor{twitterblue}{RGB}{64,153,255}
\newcommand\twitter[1]{\href{https://twitter.com/#1 }{\textcolor{twitterblue}{\faTwitter}\,\tt \textcolor{twitterblue}{@#1}}}

\submitjournal{ApJ}

@@

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
\begin{document}

\title{The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars}
\shorttitle{The Kepler Smear Campaign}
\shortauthors{B. J. S. Pope et al.}

\correspondingauthor{Benjamin J. S. Pope \twitter{fringetracker}}
\email{benjamin.pope@nyu.edu}

\author[0000-0003-2595-9114]{Benjamin J. S. Pope}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
\affiliation{NASA Sagan Fellow}
\affiliation{Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK}

\author[0000-0002-4290-7351]{Guy R. Davies}
\affiliation{School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark}

\author[0000-0002-1423-2174]{Keith Hawkins}
\affiliation{Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA}

\author[0000-0002-6980-3392]{Timothy R. White}
\affiliation{Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark}

\author[0000-0002-5496-365X]{Amalie Stokholm}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark}

\author[0000-0001-6637-5401]{Allyson Bieryla}
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}

\author[0000-0001-9911-7388]{David W. Latham}
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}

\author{Madeline Lucey}
\affiliation{Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA}

\author[0000-0003-1822-7126]{Conny Aerts}
\affiliation{Instituut voor Sterrenkunde, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium}
\affiliation{Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, NL-6500 GL Nijmegen, The Netherlands}

\author[0000-0003-1453-0574]{Suzanne Aigrain}
\affiliation{Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK}

\author[0000-0002-0865-3650]{Victoria Antoci}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark}

\author[0000-0001-5222-4661]{Timothy R. Bedding}
\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

\author[0000-0001-7402-3852]{Dominic W. Bowman}
\affiliation{Instituut voor Sterrenkunde, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium}

\author[0000-0003-1125-2564	]{Ashley Chontos}
\affiliation{Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}

\author[0000-0002-9789-5474]{Gilbert A. Esquerdo}
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}

\author[0000-0001-8832-4488 ]{Daniel Huber}
\affiliation{Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

\author[0000-0002-0722-7406]{Paula Jofr\'{e}}
\affiliation{N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile}

\author[0000-0002-5648-3107]{Simon J. Murphy}
\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

\author[0000-0003-2771-1745]{Timothy van Reeth}
\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

\author[0000-0002-6137-903X]{Victor Silva Aguirre}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

\author[0000-0002-0007-6211]{Jie Yu}
\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.

% Abstract of the paper
\begin{abstract}
We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this paper, aside from publishing the light curves of these stars, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 33 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars. We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample. \href{https://github.com/benjaminpope/smearcampaign}{\color{linkcolor}\faGithub}
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\keywords{asteroseismology -- techniques: photometric -- stars: variable: general
}

@@

% \input{quarters.tex}
\input{quarters_apj.tex}

@@

\begin{figure*}
\plotone{gaia_kepler_hr.png}

@@

\begin{figure}
\plotone{contam_HD_181778.pdf}
\caption{\label{contamination}
Power spectra of odd and even quarters of HD~181778. It is clear from inspection that while odd quarters have the power spectrum expected of a giant star, even quarters have very high amplitude coherent oscillations.}
\end{figure}

\begin{figure}
\plotone{contam.eps}

@@

% \input{all_stars.tex}
% \input{all_Stars2.tex}
\input{all_stars_apj.tex}

@@

\input{astero_table_apj.tex}

@@

\input{stellar_props_apj.tex}
\input{abundances_1_apj.tex}
\input{abundances_2_apj.tex}

@@

The spectroscopic properties are the effective temperature \teff, the metallicity \feh, and the surface gravities \logg from Table~\ref{stellar_props}. These are accompanied by the global asteroseismic properties \Dnu and \numax from Table~\ref{astero_table}. Theoretical predictions of \Dnu and \numax were computed using the asteroseismic scaling relation for any point along an evolutionary track or isochrone. For the solar values, we adopted $\nu_{\text{max, }\odot}=3090$~$\mu$Hz, $\Delta\nu_{\odot}=135.1$~$\mu$Hz \citep{huber2011}, and $T_{\text{eff, }\odot}=5777$~K.

@@

\begin{figure}
% \noindent\includegraphics[width=17cm,keepaspectratio]{different_constraints_fullsample_ove02.pdf}
\plotone{different_constraints_ben.pdf}

@@

\begin{figure}
\plotone{combined_radii.eps}

@@

\begin{figure*}
\plotone{Pope_alpha_oddZ.pdf}

@@

In addition, to the $\alpha$ and odd-Z elements we also derived the chemical abundance for several neutron capture elements including Sr, Zr, La, Eu (left panel of Fig~\ref{fig:ncap}) as well as Y, Ba, and Nd (right panel of Fig.~\ref{fig:ncap}).  It is clear from Fig.~\ref{fig:ncap}  that the chemical abundance ratio of each neutron capture element is consistent with the Galactic disk population. The Ba of our sample is slightly enhanced, however, while the Y of our sample is slightly reduced relative to the general disk population of \cite{Bensby2014}. Nevertheless, we conclude all elemental abundance ratios studied our sample most closely resemble the Galactic disk. 
\begin{figure*}
\plotone{Pope_ncap.pdf}

@@

\begin{figure*}
\plotone{HD_183124.png}

@@

\begin{figure*}
\plotone{HD186255_time-delay_plot.png}

@@

\bibliography{ms} % if your bibtex file is called example.bib

@@

% Don't change these lines
\end{document}
